<<<<<<< HEAD
---
title: "Title"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    citation_package: natbib
    latex_engine: pdflatex
header-includes:
  - \usepackage{hyperref}
  - \usepackage{titlesec}
  - \titleformat{\section}{\normalfont\Large\bfseries}{\hyperlink{toc}{\thesection}}{1em}{}
---

\newpage


```{r,include=FALSE}
#All the codes below will not show up on the knitted pdf document. 
library(Seurat)
library(monocle3)
library(SeuratData)
library(SeuratWrappers)
library(tidyverse)
library(patchwork)
library(magrittr)
library(SpatialExperiment)
library(STexampleData)
library(ggspavis)
library(scran)
library(nnSVG)
library(MerfishData)
library(ExperimentHub)
library(scater)
```

```{r,include=FALSE}
# Since we are using updated version of Seurat, make sure to change genes.tsv.gz to features.tsv.gz. 
data<-Read10X(data.dir="./")
# renamed dataset to more straight forward name. 
data2<-read.csv("merfish_all_cells.csv")
```
```{r}
ass<-list(counts=t(data2[,10:ncol(data2)]))
col<-data2[,6:8]
scn<-c("Centroid_X","Centroid_Y")
spe <- SpatialExperiment::SpatialExperiment(assays = ass, 
                                            colData = col,
                                            spatialCoordsNames = scn)
```

```{r,include=FALSE}
scRNA<-CreateSeuratObject(counts=data)
scRNA<-NormalizeData(scRNA)
scRNA<-FindVariableFeatures(scRNA)
scRNA<-ScaleData(scRNA)
scRNA<-RunPCA(scRNA)

merfish<-data2[,10:ncol(data2)]
# When running `FindVariableFeatures(), NAs are not allowed, hence removed. 
merfish<-merfish[!apply(merfish,1,function(x) any(is.na(x)|!is.numeric(x))),]
merfish_seurat<-CreateSeuratObject(counts=merfish)
merfish_seurat<-NormalizeData(merfish_seurat)
merfish_seurat<-FindVariableFeatures(merfish_seurat)
merfish_seurat<-ScaleData(merfish_seurat)
merfish_seurat<-RunPCA(merfish_seurat)

# Function to determine the number of PCA. 
elbowNum<-function(obj,threshold=.9){
  a<-obj[["pca"]]
  stdev<-a@stdev
  var<-cumsum(stdev^2)/sum(stdev^2)
  which(var>=threshold)[1]
}
# Calculates elbow point that exceeds .9, and dimension will be 1 to maximum of two seurat objects. 
n1<-elbowNum(scRNA,.9)
n2<-elbowNum(merfish_seurat,.9)
ds<-1:(max(n1,n2))

#Could not find a way to integrate. Significantly less number of samples for merfish data. 
#anchorset<-FindIntegrationAnchors(object.list=list(scRNAseq=scRNA,
#                                                   MERFISH=merfish_seurat),
#                                  dims=ds)
#seurat_int<-IntegrateData(anchorset=anchorset,dims=ds)

#Potential method is to just use one of the data instead of finding a way to integrate them together. 
```



# Abstract

## (Subsection)

### (Subsubsection)

\newpage




# Introduction

## (Subsection)

### (Subsubsection)

\newpage




# Methods

## (Subsection)

### (Subsubsection)

\newpage




# Results

## (Subsection)

### (Subsubsection)

\newpage




# Discussion

## (Subsection)

### (Subsubsection)

\newpage




# Conclusion 

## (Subsection)

### (Subsubsection)

\newpage















=======
---
title: "Title"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    citation_package: natbib
    latex_engine: pdflatex
header-includes:
  - \usepackage{hyperref}
  - \usepackage{titlesec}
  - \titleformat{\section}{\normalfont\Large\bfseries}{\hyperlink{toc}{\thesection}}{1em}{}
---

\newpage


```{r,include=FALSE}
#All the codes below will not show up on the knitted pdf document. 
library(Seurat)
library(monocle3)
library(SeuratData)
library(SeuratWrappers)
library(tidyverse)
library(patchwork)
library(magrittr)
library(SpatialExperiment)
library(STexampleData)
library(ggspavis)
library(scran)
library(nnSVG)
library(MerfishData)
library(ExperimentHub)
library(scater)
```

```{r,include=FALSE}
# Since we are using updated version of Seurat, make sure to change genes.tsv.gz to features.tsv.gz. 
data<-Read10X(data.dir="./")
# renamed dataset to more straight forward name. 
data2<-read.csv("merfish_all_cells.csv")
```
```{r}
ass<-list(counts=t(data2[,10:ncol(data2)]))
col<-data2[,6:8]
scn<-c("Centroid_X","Centroid_Y")
spe <- SpatialExperiment::SpatialExperiment(assays = ass, 
                                            colData = col,
                                            spatialCoordsNames = scn)
```

```{r,include=FALSE}
scRNA<-CreateSeuratObject(counts=data)
scRNA<-NormalizeData(scRNA)
scRNA<-FindVariableFeatures(scRNA)
scRNA<-ScaleData(scRNA)
scRNA<-RunPCA(scRNA)

merfish<-data2[,10:ncol(data2)]
# When running `FindVariableFeatures(), NAs are not allowed, hence removed. 
merfish<-merfish[!apply(merfish,1,function(x) any(is.na(x)|!is.numeric(x))),]
merfish_seurat<-CreateSeuratObject(counts=merfish)
merfish_seurat<-NormalizeData(merfish_seurat)
merfish_seurat<-FindVariableFeatures(merfish_seurat)
merfish_seurat<-ScaleData(merfish_seurat)
merfish_seurat<-RunPCA(merfish_seurat)

# Function to determine the number of PCA. 
elbowNum<-function(obj,threshold=.9){
  a<-obj[["pca"]]
  stdev<-a@stdev
  var<-cumsum(stdev^2)/sum(stdev^2)
  which(var>=threshold)[1]
}
# Calculates elbow point that exceeds .9, and dimension will be 1 to maximum of two seurat objects. 
n1<-elbowNum(scRNA,.9)
n2<-elbowNum(merfish_seurat,.9)
ds<-1:(max(n1,n2))

#Could not find a way to integrate. Significantly less number of samples for merfish data. 
#anchorset<-FindIntegrationAnchors(object.list=list(scRNAseq=scRNA,
#                                                   MERFISH=merfish_seurat),
#                                  dims=ds)
#seurat_int<-IntegrateData(anchorset=anchorset,dims=ds)

#Potential method is to just use one of the data instead of finding a way to integrate them together. 
```



# Abstract

## (Subsection)

### (Subsubsection)

\newpage




# Introduction

## (Subsection)

### (Subsubsection)

\newpage




# Methods

## (Subsection)

### (Subsubsection)

\newpage




# Results

## (Subsection)

### (Subsubsection)

\newpage




# Discussion

## (Subsection)

### (Subsubsection)

\newpage




# Conclusion 

## (Subsection)

### (Subsubsection)

\newpage















>>>>>>> 81b6d402e418eb41e61626e186982078570fc70d
